\documentclass[9pt]{article}

\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage[normalem]{ulem}
\usepackage{xcolor}

\addtolength{\topmargin}{-.25in}
\addtolength{\textheight}{0.5in}
\setlength{\parindent}{0pt}
\setlength{\multicolsep}{2pt}

\title{ASEN 6519: Optimization: Applications and Algorithms}
\author{Zachary Sunberg}
\date{Fall 2024}

\begin{document}

\maketitle

\section*{Prerequisites}

Basic knowledge of multivariable calculus, linear algebra, and probability.

\section*{Learning Objectives}

\begin{enumerate}[noitemsep]
    \item Obtain a broad understanding of models and algorithms for optimization
    \item Understand how to formulate real-world challenges as optimization problems
    \item Communicate clearly and precisely about optimization problems and results
\end{enumerate}

\section*{List of Topics}

\begin{enumerate}[noitemsep]
    \item Unconstrained local optimization (gradients, Newton's method, quasi-Newton methods)
    \item Zeroth-order optimization (derivative-free methods, evolutionary algorithms)
    \item Constraints (Lagrange multipliers, penalty methods, augmented Lagrange, interior point)
    \item Linear programming (simplex, interior point)
    \item Discrete optimization (integer programming)
    \item Additional topics as needed by students and time permits
\end{enumerate}

\section*{Textbooks}

\begin{itemize}[noitemsep]
    \item \textbf{Algorithms for Optimization} by Mykel J. Kochenderfer and Tim A. Wheeler \href{https://www.algorithmsbook.com/optimization}{(Free PDF)}
    \item \textbf{Numerical Optimization} by Jorge Nocedal and Stephen Wright \href{https://link-springer-com.colorado.idm.oclc.org/book/10.1007/978-0-387-40065-5}{(PDF access through CU Libraries)}
\end{itemize}

I may also use other books for specific topics.

\section*{Assignments and Grading}

All assignments will be submitted through gradescope. Except as noted below, you may consult any resources, including the internet, textbooks, and other students, but the final work you submit must be your own. If you use generative AI such as ChatGPT, you must disclose its use.

\begin{itemize}[noitemsep]
    \item \textbf{40\% Final Project (Report and Presentation).} (Groups of 2 permitted)
    \item \textbf{5\% Final Project Peer Review.}
    \item \textbf{20\% Homework.} (Late policy: 10\% off for first 72 hours)
    \item \textbf{15\% Research Paper Presentation.}
    \item \textbf{15\% Online Quizzes.} (Generative artificial intelligence such as ChatGPT is NOT permitted on the quizzes.)
    \item \textbf{5\% Participation.}
\end{itemize}

\subsection*{Participation Expectations}

\begin{itemize}[noitemsep]
    \item \textbf{In-person students} must attend class (I may take attendance; occasional absences due to illness or other commitments are OK, and you do not need to notify me).
    \item \textbf{Remote students} must have at least four online interactions during the semester. Interactions include attending zoom office hours, making a presentation in class, asking or answering a question on Ed, or another similar interaction.
    \item \textbf{All students} are encouraged to ask questions, participate in discussions, and engage with other classmates to understand the material.
% (Students in the in-person section are required to attend classes, and I may record attendance. Remote students )
\end{itemize}

\section*{Links}

\begin{itemize}[noitemsep]
    \item \textbf{Ed} (\href{https://edstem.org/us/courses/64118}{edstem.org/us/courses/64118}) will be the main hub for the course. All announcements will be posted there.
    \item \textbf{Gradescope} (\url{gradescope.com}) will host assignments including exact due dates.
    \item \textbf{The Schedule} is located \href{https://docs.google.com/spreadsheets/d/1WS52PyQnZtoPaRv4gSBCI2F6-yDppQboChvhXCyA8yU/edit?usp=sharing}{here}.
\end{itemize}

\section*{Instructor Contact}

Professor Zachary Sunberg\\
AERO 263 \href{mailto://zachary.sunberg@colorado.edu}{zachary.sunberg@colorado.edu}\\
\textbf{Office Hours} will be posted on Ed. I am also happy to meet individually: Please send a calendar invitation for a time not marked busy on my calendar at \url{ https://zachary.sunberg.net/contact#calendar} and indicate whether you would like to meet in my office or provide a videoconference link. \\

\section*{Meetings}

Tuesdays and Thursdays 1:00-2:15 pm\\
AERO N240

\section*{University Policies}

\begin{description}
\input{CUPolicies_Fall2024.tex}
\end{description}

\end{document}
